\chapter{Prototype Application}
\label{prototype}
In order to demonstrate practical use of the models trained in Chapter 4, a lightweight proof of concept prototype application was developed.
This application was developed for a smartphone running on the Android operating system in the Java programming language.
A backend service was created to receive an image from the smartphone
application, process the image using the CNN previously developed and return a
response to the application in the form of a prediction.

\section{Requirements}
\input{tex/prototype/requirements}

\section{Design}
\input{tex/prototype/design}

\section{Android Development}
\input{tex/prototype/android}

\section{Implementation}
\input{tex/prototype/implementation}

\section{Testing}
\input{tex/prototype/testing}

\section{Backend}
\input{tex/prototype/backend}

\section{Issues}
Some minor issues were overcame during the development of this prototype application such as:
\begin{enumerate}
	\item{Delay in image transfer: The time taken for an image to be sent to the server, be classified and return a response to the Android application was at around 12 seconds on a 4G network. This time delay was too long. In order to solve this issue, the size of the image was reduced from approimately 3000x4000 pixels to an image size of 300x400 pixels. This resulted in the time delay reducing to 3 or 4 seconds.}
	\item{Service failure on backend: The backend instance service was stopping in a seemlingly random fashion. This was due to an incomoatibility with Python FLASK and the nohup (ignores the hangup signal in Linux) command used to deploy the FLASK application. To resolve this issue screen was used to run the app using a simple command 'python server.py'.}
	\item{Perfomance issues: The Android application was facing some performance issues when displaying the food logs. The UI would temporarily freeze. This was because too much work was being carried out on the main thread. To combat this, another thread was created to complete the task.}
\begin{enumerate}