\chapter{Background}
\label{background}

This chapter outlines background information on the subject of nutritional assessment using computer vision.
An overview of neural networks is explored, followed by a literature review of the subject area.
Analysis into evaluating the efficacy of CNNs is covered and finally a conclusion to the information gained.

\input{tex/background/introToMl}

\input{tex/background/neuralComputing}

\input{tex/background/cnnOverview}

\input{tex/background/cnnExtensions}

\input{tex/background/svm}

\section{Evaluating the Output}
\input{tex/background/eval}

\input{tex/background/dietary}

\section{Object Detection Using CNNs}
\input{tex/background/rcnn}

\section{APIs and Libraries}
\tocless\subsection{TensorFlow}
\input{tex/tech/tensorflow}

\tocless\subsection{OpenCV}
\input{tex/tech/opencv}

\tocless\subsection{NumPy}
\input{tex/tech/numpy}

\section{Public Domain Datasets}
\input{tex/background/datasets}

\section{Conclusion}
This chapter has covered a comprehensive survey of literature along with an overview of the underlying concepts to the approaches used in the literature..
This survey has covered the topics of using CNNs, SVMs and other methods for nutritional assessment.
Topics also covered include evaluating the output, object detection using CNNS, neural computing, an overview of CNNS and SVMS and an overview of the technologies used in this project.

From the literature review, there are many different approaches that have been promising in the area of using deep learning for nutritional assessment.
It has been decided to attempt to replicate the work carried out by \parencite{yanaiFood} with some modifications that will be outlined in the following chapters.
While this approach will be attempted, there are many viable options that can still be investigated for future work.


