\section{Neural Computing}
The main area of my focus for this project is in
Artificial Neural Networks (ANN). This is because extensive research has been carried out into Convolutional Neural Networks (CNNs) which are based on ANNs.
\subsection*{Artificial Neural Networks}
An Artificial Neural Network is a bio-inspired system that is used to model the human brain in how it learns from experience.
ANNs were first introduced in 1943 and were studied until the 1960's when the concept was shelved and revived gain in the 1980's \parencite{handsOnML}.
The ANN uses this model to build a very complex web of connected units called
artificial neurons.
These neurons are connected by certain weights which determines the processing
capacity of the network and these weights are created by learning a
dataset \parencite{malachy}.
An neuron has a set of inputs that take in a value, sometimes from network outputs
and produce a single result or classification.

As stated above, an ANN is bio-inspired from biological neurons \parencite{handsOnML}.
Biological neurons are cells located in animals brains.
These neurons receive signals (electrical impulses) from other neurons and fires their own signal thereafter.
While an individual neuron is very simple, millions of these neurons working together can result in very complex computations.
From this, an artificial neuron was proposed through a simple model which had a binary input (1 or more) and a single binary output.


Before Convolution Neural Networks can be explored, which are vital to image
processing, the perceptron learning algorithm, the multi
layer perceptron, backpropogation must be analysed.

\input{tex/background/perceptron}

\input{tex/background/gD_bP}